--- 
title: "Bookdown Project"
author: "Nora Stanley"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: 
  bookdown::gitbook:
    config:
      sharing:
        facebook: false
        twitter: false
documentclass: book
bibliography: [bibliography.bib]
biblio-style: apalike
link-citations: yes
github-repo: https://github.com/ericmkeen/bookdown_minimal
description: "This is my bookdown project for data story #3, a foundation for my final data story project"
---

# Prerequisites

This is my bookdown project for data story #3, a foundation for my final data story project.

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$, or for weaving in `R` with `Rmarkdown`.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
library(bookdown)
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
